\documentclass[12pt]{report}
\usepackage[utf8]{inputenc}
\usepackage{graphicx,listings,verbatim,csquotes,amsmath}
\usepackage[backend=bibtex]{biblatex}
\usepackage[margin=1in]{geometry}
\addbibresource{Thesis.bib}

\begin{document}

\title{
	{Algorithms and Applications of the Vision Correcting Display}\\
	{\large University of California, Berkeley}\\
}
\author{Charles Ding}
\date{12 May 2017}

\maketitle

\chapter*{Abstract}
Human vision problems such as nearsightedness and farsightedness are a result of optical aberrations in the human eye. The common method of treating eye aberrations is wearing corrective lenses, such as glasses or contact lenses, or undergoing laser eye surgery. The vision correcting display team under Professor Brian Barsky aims to develop a light field display using hardware and software that lets the user see a digital screen clearly without glasses or contact lenses. In addition, the team writes software simulations of the vision correcting display to evaluate the performance of the display for different eye aberrations and different digital devices. \\
In this paper, we present a new software approach to the display, the backward method, and compare it with the original light field algorithm \cite{Huang:EECS-2013-206} and the forward method \cite{Wu:EECS-2016-67}. We also explore two new applications of the vision correcting display: the effect of different pixel arrangements from different devices on the performance of the display and the effects of diffraction in choosing an optimal pinhole size. Finally, we present a new approach to the software simulation that combines both ray and wave optics.

\chapter*{Acknowledgements}
I want to thank my advisor Professor Brian Barsky for all his help and support during my two years as a member of his research group. Also, I want to thank all the members of the vision correcting display team, especially Michael Chen, Dingyi Zheng, Linghan Zheng, Tongyu Chen, Luxin Yang, Haonan Jing, Hung Vu, and Yirong Zhen for all their help and contributions. Finally, I want to thank Professor Laura Waller for helping me look over my thesis and teaching the computational imaging class that I took.

\tableofcontents

\input{chapters/chapter1/introduction}

\input{chapters/chapter2/chapter2}

\input{chapters/chapter3/chapter3}

\input{chapters/chapter4/chapter4}

\input{chapters/chapter5/chapter5}

\input{chapters/chapter6/chapter6}

\input{chapters/chapter7/chapter7}

\input{chapters/chapter8/chapter8}

\input{chapters/chapter9/chapter9}

\input{chapters/chapter10/chapter10}

\printbibliography

\end{document}